The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-02-28 RET_Hosts.tex

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
 %M. Pursiainen$^1$,
 %M. J. Childress$^1$,
 %M. Smith$^1$,
 and Other Authors$^{1,2}$,
\newauthor
(The DES Collaboration)
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
$^{2}$Other Institutions\\
%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

@@

\subsection{Improvements to the search method}

\miika{Miika to verify!}
The original method of finding RETs in the DES-SN data (and presented in \citetalias{Pursiainen2018}) was designed to be simple and used light curve modelling with Gaussian and linear fits. The simplistic method made it possible to look for exotic transients without knowing their observed characteristics beforehand and resulted in a large sample of photometrically selected fast transients. However, as the search was simplistic and relied heavily on visual inspection of the available data (etc. images, light curves, host galaxy information), it is impossible to be sure how complete the sample is. For instance, due to the large redshift range within the sample it is entirely possible that distant events could have been missed due to time dilation. Here, a more sophisticated search method is presented. As only a fraction of transients in DES-SN have redshift information from host galaxy, the search must be done in the observer frame.  The key features of RETs that distinguishes them from most traditional SNe types are the fast light curve evolution and blue colour at peak. Even though both of these quantities depend on the redshift of the transient, they still seem to distinguish the the fast events from traditional SN types.

To assess the distinguishing photometric properties of RETs, we take the sample of 72 \textcolor{green}{(92)} from the \citetalias{Pursiainen2018} method along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
\begin{enumerate}
\item The transient was only detected in one DES-SN observing season.
\item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields).
\item $g$- and $r$-band observations used for the colour had to be taken within 2 days in observer frame.
\end{enumerate}

Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame. However, using photometric data points directly has several problems that can be improved. For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases. Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range. To negate this issue, we interpolate the light curves using the method of Gaussian processes (GP). \textcolor{green}{(To negate this issue, we use the interpolated GP LCs presented in Pursiainen et al. 2019)} The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band. Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig. \ref{fig:selection}) and are thus easier to separate. We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness). The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig. \ref{fig:selection}.

We process all $\sim 30,000$ DES-SN transient candidates with GP. In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier which we train on spectrosopically confirmed objects, and use to separate the sample into two subtypes: AGN-like and SNe-like. The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are likely removed by the final manual vetting. \textcolor{green}{(I'll find the list of AGN and find out where they are from.)}
The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs. These objects are subject to a further set of cuts. We impose a cut based on a fit of the LC with the \texttt{PSNID} software (\citet{Sako2008}). We use thresholds of \texttt{FITPROB}$<0.91$ and \texttt{PBAYES}$<0.82$ to remove highly-probably SNe Ia, which removes 46 objects from the RET parameter space. In order to further remove longer-lived SNe, the decline time to half of the peak brightness must be $<24$ days. This removes 347 SNe, resulting in 546 objects remaining inside the parameter space. The final 564 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.

Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14. \textcolor{green}{The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.}
We refer to the resulting sample as DES RETs. Of the 106 objects in the sample, 97 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift. A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves. We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra. The observational properties of the 49 hosts with redshift are displayed in Table \ref{tab:obs}.

@@

\toprule
{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
Transient name &          &           &          &         &         &            &               \\
\midrule
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
DES13S2wxf     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
DES13X3gmd     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
DES13C3uig     & 52.94416 & -27.58544 & $22.17 \pm 0.03$ & 0.6734 &       ACES &               \\
DES13X2wvv     & 34.86526 &  -6.71603 & $21.89 \pm 0.02$ & 0.4750 &      OzDES &       4.50 \\
DES14S2anq     & 41.27776 &  -0.74529 & $17.57 \pm 0.03$ & 0.0521 &      OzDES &       0.75 \\
DES14X1bnh     & 33.74902 &  -4.79254 & $21.95 \pm 0.03$ & 0.8298 &      OzDES &       3.50 \\
DES15S1fli     & 43.18790 &  -0.88620 & $20.98 \pm 0.02$ & 0.4473 &      OzDES &       2.33 \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\end{tablenotes}
\end{threeparttable}
\end{center}
\label{tab:obs}
\end{table*}
\begin{figure*}
\includegraphics[width=\textwidth]{figs/gal_spec.png}
\caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
\label{fig:host_spec}}
\end{figure*}

@@

@@

@@

Other local rapid transients include SN2018gep \citep{Ho2019}, a spectroscopically classified SN Ic-bl with a rapid rise. The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR. The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}. SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic. While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host.

\subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}
In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of DES16C1cbd appears to be a passive galaxy
\section{Conclusions}

@@

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

>>>>

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\hgamma}[0]{H$\gamma$}
\newcommand{\hdelta}[0]{H$\delta$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[RET host galaxies in DES]{The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
 %M. Pursiainen$^1$,
 %M. J. Childress$^1$,
 %M. Smith$^1$,
 %E. Swann$^2$,
 and Other Authors$^{1,2,3}$,
\newauthor
(The DES Collaboration)
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
$^{2}$Other Institutions\\
%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

\toprule
{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time (hours) \tnote{b} \\
Transient name &          &           &          &         &         &            &               \\
\midrule
DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    \tnote{d} &          - &             - \\
DES13S2wxf\tnote{e}     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    \tnote{c} &      OzDES &             - \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    \tnote{d} &          - &             - \\
DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\item[c] Host targetted by OzDES but no redshift measurement possible.
\item[d] Host not targetted by OzDES
\item[e] Found by updated search method (Section \ref{subsec:new_method})
\end{tablenotes}
\end{threeparttable}
\end{center}
\label{tab:obs}
\end{table*}

@@

\subsection{Improvements to the search method \label{subsec:new_method}}

\miika{Miika to verify!}
The original method of finding RETs in the DES-SN data (and presented in \citetalias{Pursiainen2018}) was designed to be simple and used light curve modelling with Gaussian and linear fits. The simplistic method made it possible to look for exotic transients without knowing their observed characteristics beforehand and resulted in a large sample of photometrically selected fast transients. However, as the search was simplistic and relied heavily on visual inspection of the available data (etc. images, light curves, host galaxy information), it is impossible to be sure how complete the sample is. For instance, due to the large redshift range within the sample it is entirely possible that distant events could have been missed due to time dilation. Here, a more sophisticated search method is presented. As only a fraction of transients in DES-SN have redshift information from host galaxy, the search must be done in the observer frame.  The key features of RETs that separate them from most traditional SNe types are the fast light curve evolution and blue colour at peak. Even though both of these quantities depend on the redshift of the transient, they still seem to distinguish the the fast events from traditional SN types.

To assess the unique photometric properties of RETs, we take the sample of 72 from the \citetalias{Pursiainen2018} method, updated with 20 extra objects found using that method in the fifth season of DES, along with spectroscopically confirmed SNe of types Ia, Ibc, II, and SLSNe from DES that pass the following criteria:
\begin{enumerate}
\item The transient was only detected in one DES-SN observing season.
\item Maximum observed brightness in both $g$- and $r$-bands was brighter than 24 mag (in the eight `shallow' DES-SN fields) or 25 mag (in the two `deep' fields).
\item $g$- and $r$-band observations used for the colour had to be taken within 2 days in observer frame.
\end{enumerate}

Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame. However, using photometric data points directly has several problems that can be improved. For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases. Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range. To negate this issue, we use the interpolated GP LCs presented in \citet{Pursiainen2019}. The interpolated light curves have a 0.5 day cadence and every epoch has a flux value, and an associated uncertainty, for each band. Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$-$t_{\mathrm{rise; r}}$ parameter space (Fig. \ref{fig:selection}) and are thus easier to separate. We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness). The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig. \ref{fig:selection}.

We process all $\sim 30,000$ DES-SN transient candidates with GP. In order to reduce the contamination from active galactic nuclei (AGN), we use a basic convolutional neural network (CNN) classifier. We train the CNN on spectrosopically confirmed SNe of all types and on spectroscopically typed AGN, and use it to separate the sample into two photometric subtypes: AGN-like and SNe-like. The classifier returns SNe-like objects with an accuracy of 0.992 on the test set; the remaining AGN are removed by the final manual vetting. \textcolor{green}{(I'll find the list of AGN and find out where they are from.)}
The SNe passing the CNN classifier are subjected to the LC quality cuts, resulting in 2259 objects, of which 939 lie inside the colour and rise-time region which we defined as RETs. These objects are subject to a further set of cuts. We impose a cut based on a fit of the LC with the \texttt{PSNID} software (\citet{Sako2008}). We use thresholds of \texttt{FITPROB}$<0.91$ and \texttt{PBAYES}$<0.82$ to remove highly-probably SNe Ia, which removes 46 objects from the RET parameter space. In order to further remove longer-lived SNe, the decline time to half of the peak brightness must be $<24$ days. This removes 347 SNe, resulting in 546 objects remaining inside the parameter space. The final 564 transients have been visually inspected, with the majority rejected for being spurious detections, obvious multi-season variability that was not picked up by the CNN, or showing evidence for a longer timescale decline.

Using the above method recovers 87 of the 92 RETs found using the \citetalias{Pursiainen2018} technique, and adds a further 14. The five were not recovered as their GP lightcurves were fainter than the limits given above in either g or r band.
We refer to the resulting sample as DES RETs. Of the 106 objects in the sample, 97 have a host galaxy detected in deep host galaxy photometry of \citet{Wiseman2020}, of which 49 have a host galaxy spectroscopic redshift. A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves. We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra. The observational properties of the 49 hosts with redshift are displayed in Table \ref{tab:obs}.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/gal_spec.png}
\caption{The spectrum of DES16C2ggt, decomposed into its constituent components according to the \texttt{pPXF} fit. 
\label{fig:host_spec}}
\end{figure*}

@@

\begin{table*}

\caption{Host galaxy properties for the 49 DES RET host galaxies with redshifts and host galaxy spectra. The full table is available online in the online version in a machine readable format.}
\begin{threeparttable}
\begin{tabular}{lrrrllllll}
\toprule
Transient Name &$\log \left(M_*\right)$ &$\log \left(\mathrm{SFR}\right)$ &  $\log \left(\mathrm{sSFR}\right)$ &                                                           \multicolumn{6}{c}{$12+\log\left(\mathrm{O/H}\right)\tnote{a} $}\\
%\midrule
{} & $\left( M_{\odot}\right)$ & $\left(M_{\odot} \mathrm{yr}^{-1}\right)$&$\left(M_{\odot}\ \mathrm{yr}^{-1} M_{\odot}^{-1}\right)$& Best &                                                           D16 &                                                       PP04 N2 &                                                     PP04 O3N2 &                                                      KK04 R23 &                                                   Average O3N2\tnote{b}\\
\midrule
DES13X3gms &   $9.41 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.27}$ &  $-0.06 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.78}$ &   $-9.47 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.52}$ &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &                                                             - &                                                             - &                                                             - &  $8.55 _{\scriptscriptstyle 0.86} ^{\scriptscriptstyle 0.37}$ &   $8.22 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.35}$ \\
DES13C1tgd &  $10.24 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.08}$ &   $0.10 _{\scriptscriptstyle 0.47} ^{\scriptscriptstyle 0.38}$ &  $-10.14 _{\scriptscriptstyle 0.39} ^{\scriptscriptstyle 0.30}$ &  $8.64 _{\scriptscriptstyle 0.06} ^{\scriptscriptstyle 0.06}$ &  $8.59 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &  $8.68 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &   $8.75 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
DES13S2wxf &   $9.86 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.06}$ &   $0.29 _{\scriptscriptstyle 0.07} ^{\scriptscriptstyle 0.10}$ &   $-9.57 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &                                                             - &                                                             - &                                                             - &  $8.58 _{\scriptscriptstyle 0.58} ^{\scriptscriptstyle 0.27}$ &   $8.25 _{\scriptscriptstyle 0.25} ^{\scriptscriptstyle 0.25}$ \\
DES13X1hav &   $9.16 _{\scriptscriptstyle 0.16} ^{\scriptscriptstyle 0.38}$ &  $-0.44 _{\scriptscriptstyle 0.37} ^{\scriptscriptstyle 0.93}$ &   $-9.60 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.55}$ &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &                                                             - &                                                             - &                                                             - &  $8.51 _{\scriptscriptstyle 0.75} ^{\scriptscriptstyle 0.39}$ &   $8.20 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.36}$ \\
DES13E2lpk &  $10.66 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.10}$ &   $0.46 _{\scriptscriptstyle 0.36} ^{\scriptscriptstyle 0.45}$ &  $-10.20 _{\scriptscriptstyle 0.27} ^{\scriptscriptstyle 0.35}$ &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &                                                             - &                                                             - &                                                             - &  $8.92 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ &   $8.58 _{\scriptscriptstyle 0.03} ^{\scriptscriptstyle 0.03}$ \\
DES15C2eal &   $8.42 _{\scriptscriptstyle 0.09} ^{\scriptscriptstyle 0.18}$ &  $-1.29 _{\scriptscriptstyle 0.30} ^{\scriptscriptstyle 0.33}$ &   $-9.72 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.15}$ &  $8.29 _{\scriptscriptstyle 0.35} ^{\scriptscriptstyle 0.25}$ &  $7.97 _{\scriptscriptstyle 0.51} ^{\scriptscriptstyle 0.29}$ &  $8.29 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.15}$ &  $8.34 _{\scriptscriptstyle 0.20} ^{\scriptscriptstyle 0.15}$ &  $8.52 _{\scriptscriptstyle 0.49} ^{\scriptscriptstyle 0.57}$ &   $8.28 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.30}$ \\
DES16C2ggt &   $9.86 _{\scriptscriptstyle 0.29} ^{\scriptscriptstyle 0.36}$ &   $0.13 _{\scriptscriptstyle 0.46} ^{\scriptscriptstyle 0.94}$ &   $-9.73 _{\scriptscriptstyle 0.18} ^{\scriptscriptstyle 0.59}$ &  $8.53 _{\scriptscriptstyle 0.15} ^{\scriptscriptstyle 0.39}$ &  $8.37 _{\scriptscriptstyle 0.04} ^{\scriptscriptstyle 0.04}$ &  $8.51 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &  $8.54 _{\scriptscriptstyle 0.01} ^{\scriptscriptstyle 0.01}$ &  $8.93 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ &   $8.56 _{\scriptscriptstyle 0.02} ^{\scriptscriptstyle 0.02}$ \\
DES17C2hno &   $9.56 _{\scriptscriptstyle 0.21} ^{\scriptscriptstyle 0.16}$ &  $-0.02 _{\scriptscriptstyle 0.44} ^{\scriptscriptstyle 0.33}$ &   $-9.58 _{\scriptscriptstyle 0.24} ^{\scriptscriptstyle 0.17}$ &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &                                                             - &                                                             - &                                                             - &  $8.94 _{\scriptscriptstyle 0.17} ^{\scriptscriptstyle 0.09}$ &   $8.60 _{\scriptscriptstyle 0.19} ^{\scriptscriptstyle 0.11}$ \\

\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Linear combination of the likelihoods for D16, PP04 N2, PP04 O3N2, KK04 R23.
\item[b] Weighted average of PP04 N2, PP04 O3N2, and KK04 R23, where N2 and R23 were converted to PP04 O3N2 via \citet{Kewley2008}.

\end{tablenotes}
\end{threeparttable}
\label{tab:derived}
\end{table*}

@@

Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the results from the probability density functions (PDFs) of the various different diagnostics, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and display the results in Table \ref{tab:derived}.

@@

Other local rapid transients include SN2018gep \citep{Ho2019}, a spectroscopically classified SN Ic-bl with a rapid rise. The host of SN2018gep appears more similar to the DES RET sample, lying in the same $M_*$-SFR and $M*$-sSFR plane, as well as lying below the MZR. While the SN2018gep host is lower in stellar mass than any DES RET ($\log \left(M/M_{\odot}\right) =8.11$, galaxies of that mass are unlikely to have been detected at the redshifts of the DES RETs \citep{Wiseman2020}. The authors' conclusion that SN2018gep is related to a shock-breakout of a massive, stripped-envelope star is similar to that posited in Section \ref{subsec:disc_origin}. SN2018kzr \citep{McBrien2019} is one of the most rapidly declining transients ever discovered, with spectral signatures similar to SNe Ic. While host galaxy properties are not derived, the authors of that paper refer to narrow emission from the host galaxy, along with an apparently small, blue, star-forming host.

\subsection{The passive host of DES16C1cbd \label{subsec:disc_cbd}}
In Figs. \ref{fig:sfms_sfr} and \ref{fig:sfms_ssfr} there is one clear outlier with very low SFR. The host of DES16C1cbd appears to be a passive galaxy

\phil{Adding more once I know about the SFR from [OII]}
\section{Conclusions}

@@

\section{Spectral line fluxes}
\begin{table*}
\caption{Emission line fluxes for DES RET host galaxies. Values are given in units of erg/cm/s/\AA, and have been corrected for Milky Way reddening using \citet{Schlegel1998}, assuming a \citet{Cardelli1989} with $R_V = 3.1$, but not for intrinsic host galaxy reddening.}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{llllllllllll}
\toprule
{} &              \OII 3727 &             \OIII 4960 &              \OIII 5007 &             \NII 6549 &             \NII 6585 &             \SII 6717 &             \SII 6731 &           \hdelta &            \hgamma &             \hbeta &            \halpha \\
\midrule
DES13X3gms &  $43.3 \pm 27.7$ &   $10.9 \pm 7.9$ &    $32.9 \pm 7.9$ &               - &               - &               - &               - &   $2.0 \pm 7.6$ &   $17.0 \pm 7.1$ &    $6.3 \pm 9.5$ &                - \\
DES13C1tgd &    $1.9 \pm 0.7$ &    $0.0 \pm 0.1$ &     $0.0 \pm 0.1$ &   $0.5 \pm 0.1$ &   $1.6 \pm 0.1$ &   $1.1 \pm 0.0$ &   $0.8 \pm 0.0$ &   $0.9 \pm 0.2$ &    $1.3 \pm 0.1$ &    $0.2 \pm 0.1$ &    $4.5 \pm 0.2$ \\
DES13S2wxf &   $22.1 \pm 5.3$ &    $3.2 \pm 2.0$ &     $9.8 \pm 2.0$ &               - &               - &               - &               - &   $2.4 \pm 1.0$ &    $4.3 \pm 0.8$ &    $4.5 \pm 2.1$ &                - \\
DES13X1hav &  $31.4 \pm 49.1$ &  $10.5 \pm 12.0$ &   $31.9 \pm 12.0$ &               - &               - &               - &               - &   $0.0 \pm 6.2$ &   $5.2 \pm 11.5$ &   $10.6 \pm 4.8$ &                - \\
DES13X3nyg &   $15.1 \pm 1.6$ &    $3.2 \pm 0.4$ &     $9.8 \pm 0.4$ &               - &               - &               - &               - &   $0.5 \pm 0.4$ &    $0.0 \pm 0.6$ &    $3.3 \pm 0.4$ &                - \\
DES13X3gmd &   $18.8 \pm 5.3$ &                - &                 - &               - &               - &               - &               - &   $1.9 \pm 3.8$ &    $2.3 \pm 2.7$ &    $7.0 \pm 8.3$ &                - \\
DES13X2wvv &  $61.5 \pm 14.4$ &    $7.4 \pm 3.6$ &    $22.6 \pm 3.6$ &               - &               - &               - &               - &   $2.7 \pm 4.9$ &    $1.1 \pm 3.3$ &   $10.3 \pm 2.8$ &                - \\
DES14S2anq &  $486.0 \pm 0.4$ &   $74.9 \pm 1.1$ &   $227.1 \pm 1.1$ &  $10.3 \pm 5.1$ &  $31.1 \pm 5.1$ &  $43.1 \pm 4.0$ &  $31.1 \pm 4.5$ &  $31.5 \pm 1.4$ &   $58.9 \pm 1.4$ &  $114.0 \pm 1.4$ &  $240.0 \pm 0.9$ \\
DES14X1bnh &   $23.1 \pm 1.2$ &                - &                 - &               - &               - &               - &               - &   $0.4 \pm 0.4$ &    $3.1 \pm 0.5$ &                - &                - \\
DES15S1fli &   $33.3 \pm 3.3$ &    $3.4 \pm 1.5$ &    $10.5 \pm 1.5$ &               - &               - &               - &               - &   $3.0 \pm 1.5$ &    $4.2 \pm 0.8$ &    $8.7 \pm 0.4$ &                - \\
DES15S1fll &  $75.2 \pm 78.8$ &  $13.6 \pm 10.8$ &   $41.3 \pm 10.8$ &   $1.4 \pm 3.9$ &   $4.4 \pm 3.9$ &   $2.7 \pm 2.6$ &   $4.9 \pm 2.8$ &  $0.6 \pm 19.2$ &  $14.3 \pm 16.6$ &  $13.4 \pm 10.2$ &   $40.9 \pm 5.2$ \\
DES14X3pkl &   $13.5 \pm 9.5$ &    $2.6 \pm 0.8$ &     $7.9 \pm 0.8$ &   $0.7 \pm 0.4$ &   $2.2 \pm 0.4$ &   $3.5 \pm 0.5$ &   $1.9 \pm 0.3$ &   $1.7 \pm 2.7$ &    $2.6 \pm 2.8$ &    $0.0 \pm 2.1$ &   $10.4 \pm 0.7$ \\
DES13X3npb &   $14.6 \pm 4.1$ &    $1.4 \pm 0.2$ &     $4.2 \pm 0.2$ &               - &               - &               - &               - &   $2.3 \pm 0.2$ &    $4.0 \pm 0.2$ &    $5.7 \pm 0.2$ &                - \\
DES15X2ead &   $9.7 \pm 10.0$ &    $0.8 \pm 0.8$ &     $2.3 \pm 0.8$ &   $0.8 \pm 0.4$ &   $2.5 \pm 0.4$ &   $3.5 \pm 0.3$ &   $2.2 \pm 0.6$ &   $2.9 \pm 2.5$ &    $1.3 \pm 1.7$ &    $2.3 \pm 0.8$ &   $11.5 \pm 0.3$ \\
DES14S2plb &   $14.1 \pm 0.7$ &    $1.0 \pm 0.1$ &     $3.0 \pm 0.1$ &   $1.2 \pm 0.0$ &   $3.6 \pm 0.0$ &   $2.3 \pm 0.0$ &   $1.8 \pm 0.0$ &   $2.0 \pm 0.1$ &    $2.3 \pm 0.1$ &    $4.8 \pm 0.1$ &   $12.2 \pm 0.0$ \\
DES14S2pli &   $13.7 \pm 0.9$ &    $0.6 \pm 0.1$ &     $1.7 \pm 0.1$ &               - &               - &               - &               - &   $0.0 \pm 0.4$ &    $1.6 \pm 0.3$ &    $3.5 \pm 0.1$ &                - \\
DES14C3tnz &   $23.1 \pm 4.5$ &    $3.0 \pm 1.0$ &     $9.2 \pm 1.0$ &               - &               - &               - &               - &   $1.1 \pm 0.9$ &    $4.5 \pm 1.5$ &    $4.4 \pm 3.8$ &                - \\
DES15X3mxf &   $29.5 \pm 3.4$ &    $1.7 \pm 0.5$ &     $5.2 \pm 0.5$ &               - &               - &               - &               - &   $1.1 \pm 2.8$ &    $4.0 \pm 1.2$ &    $5.0 \pm 0.5$ &                - \\
DES15C3lpq &   $37.0 \pm 9.8$ &    $8.6 \pm 3.3$ &    $26.2 \pm 3.3$ &               - &               - &               - &               - &   $4.2 \pm 2.6$ &    $2.3 \pm 2.6$ &    $9.1 \pm 4.5$ &                - \\
DES15C3nat &   $21.6 \pm 1.5$ &                - &                 - &               - &               - &               - &               - &   $1.5 \pm 0.6$ &    $4.2 \pm 1.4$ &                - &                - \\
DES15C3mgq &  $17.0 \pm 20.8$ &    $6.3 \pm 2.4$ &    $19.1 \pm 2.4$ &   $0.4 \pm 1.3$ &   $1.3 \pm 1.3$ &   $1.2 \pm 0.7$ &   $0.0 \pm 3.6$ &   $1.8 \pm 5.1$ &    $1.7 \pm 4.0$ &    $6.2 \pm 2.9$ &   $10.6 \pm 0.8$ \\
